Storm Surges

### 2014-05-06 RoughWork/manuscript.tex
Added description of CGRF.

\subsubsection{Sea Surface Height}
Sea surface height at the mouth of Juan de Fuca was set using values from the Tofino tide gauge.  A monthly climatology was produced using daily averages from 2000-2010, binning them by month, averaging and setting the yearly mean to zero.  For the storm surge simulations, hourly variations in sea surface height were used.  These values are the Tofino tide gauge values, de-tided and with the zero reset as for the climatology.

@@

\subsection{Atmospheric forcing}

>>>>

\subsubsection{Sea Surface Height}
Sea surface height at the mouth of Juan de Fuca was set using values from the Tofino tide gauge.  A monthly climatology was produced using daily averages from 2000-2010, binning them by month, averaging and setting the yearly mean to zero.  For the storm surge simulations, hourly variations in sea surface height were used.  These values are the Tofino tide gauge values, de-tided and with the zero reset as for the climatology. The storm surge simulations also used the sea surface height anomaly from Port Hardy, forced at the northern boundary in Johnstone Strait.

@@

\subsection{Atmospheric forcing}
The ocean surface is forced with momentum and heat fluxes from a 33-km global atmospheric reforcasting model suitable for use in ocean modelling \citep{smith2013new}. Forecasts from the period of 2002-2011 are available. Additionally, the inverse barometric effect of the atmospheric pressure is included, an important consideration in storm surge modelling.
